%-------------------------
% Resume in Latex
% Author : Supratim Mondal
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

% Some page-style/margin packages may reset \footskip at begin-document.
\AtBeginDocument{\setlength{\footskip}{10pt}}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      	\textbf{#1} & #2 \\
      	\textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://smrk.in}{\Large Supratim Mondal}} & Email : \href{mailto:mail@smrk.in}{mail@smrk.in}\\
  \href{https://smrk.in}{{https://smrk.in}} & \\
\end{tabular*}


%-----------SUMMARY-----------------
\section{Summary}
  \resumeSubHeadingListStart
    \item\small{Final-year Electronics \& Communication Engineering student passionate about embedded systems and full-stack IoT. Experienced in bridging the gap between hardware and software, from designing PCBs and writing firmware to integrating devices with responsive cloud dashboards. Actively engaged in renewable energy research and hands-on network deployments.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. B. C. Roy Engineering College}{Durgapur, West Bengal}
      {B.Tech in Electronics \& Communication Engineering (ECE); Final-year (Batch 2026)}{Expected Jun. 2026}
  \resumeSubHeadingListEnd


%--------SKILLS---------------------
\section{Technical Skills}
 \resumeSubHeadingListStart
  \small
  \item{\textbf{Embedded Firmware}{: C/C++, Arduino Framework, ESP-IDF, Python (Scripting).}}
  \item{\textbf{Hardware Design}{: PCB Layout \& Schematic (KiCad, Altium, EasyEDA), Circuit Analysis, Soldering \& Rework.}}
  \item{\textbf{Telecom \& Networking}{: 5G and FTTx deployments, failsafe design, telecom-grade routing \& switching.}}
  \item{\textbf{IoT \& Cloud}{: MQTT, HTTP/REST, Firebase/GCP, AWS, Azure, Docker.}}
  \item{\textbf{Web Development}{: JavaScript/TypeScript, Next.js, Express, React, PostgreSQL.}}
  \item{\textbf{Lab Instruments}{: Oscilloscope, Multimeter, Logic Analyzer, Bench Power Supply.}}
 \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BSNL}{Burdwan, West Bengal}
      {Telecommunications Intern}{Summer 2025}
      \resumeItemListStart
        \resumeItem{Routing \& Switching}
          {Analyzed telecom-grade routing and switching protocols used in live networks.}
        \resumeItem{Field Support}
          {Assisted field engineers in troubleshooting signal integrity issues for fiber optic endpoints.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Power SDI (PMSGY)}{Maithon, Jharkhand}
      {Supervising Engineer Trainee}{Winter 2026}
      \resumeItemListStart
        \resumeItem{Training Focus}{Supervised solar PV cell installation, safety compliance, and on-site commissioning.}
        \resumeItem{Site Work}{Assisted in PV site surveys, panel mounting, and safety inspections.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeHeading{Implementation of 800W MPPT using ESP32 for Rural Electrification}{Academic}{ESP32 $\bullet$ MPPT $\bullet$ Incremental Conductance}{Winter 2026}
      \resumeItemListStart
        \resumeItem{Overview}{Designed and implemented an 800W synchronous MPPT solar charge controller to improve conversion efficiency for rural electrification and smart energy management.}
      \resumeItemListEnd

    \resumeHeading{Intelligent Smart Grid \& Energy Telemetry Platform}{Academic}{Edge Computing $\bullet$ Power Metrology $\bullet$ Real-Time Cloud DB $\bullet$ Web Framework}{Fall 2025}
      \resumeItemListStart
        \resumeItem{Overview}{Microcontroller-driven prepaid energy meter streaming real-time telemetry to a secure cloud database and a responsive web dashboard.}
        \resumeItem{Key Results}{Implemented high-precision metering and remote relay cutoff with local response $<200$ms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------RESEARCH & PUBLICATIONS-----------------
\section{Research \& Publications}
  \resumeSubHeadingListStart
    \resumeHeading{Weather-Integrated PEMS for Residential Hybrid Solar Installations}{Electrica journal}{Under Review (Submission ID: electr-2025-0424)}{Winter 2025}
      \resumeItemListStart
        \resumeItem{Overview}{Predictive energy management for residential hybrid solar using weather inputs and smart metering to improve scheduling and efficiency.}
      \resumeItemListEnd

    \resumeHeading{ESP32-Based Synchronous MPPT SCC with INC Algorithm}{ICICET 2026}{Accepted for Presentation (Speaker Category, Track 7)}{Aug. 2026}
      \resumeItemListStart
        \resumeItem{Overview}{Abstract accepted for presentation at Bolpur, Shantiniketan. Demonstrated high conversion efficiency and strong applicability in renewable energy systems for rural electrification.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
  %-----------INTERESTS-----------------
\section{Interests}
 \resumeSubHeadingListStart
  \resumeSubItem{Audio stories; DIY electronics projects; Solar \& renewable tech; Reading research papers; Open-source; Fixing family electronics; Working on}{https://toolhub.live}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
